Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-12 ltx/data_paper/DataPaper.tex
edit to result section

The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function. However, to compute the supports the unknown parameters, $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.  To form a more accurate initial guess of the unkown parameters and explore the effect on the estimated support several tests were performed. First consider equation \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function. As mentioned before the power spectral densities are non negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$. The minimum value of the power spectral density was 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit. This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted. The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and thresholded for values less than 0.01. By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using equation \eqref{eq:EM-AnalyticSupportCalculation}. Deconvolution can also be performed numerically to directly find the support as can be seen in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.

>>>>

The correlation analysis described in Section \ref{subsec:CorrAnal} were applied to generated data in order to approximate the unknown supports of both connectivity kernel and the disturbance covariance function. However, to compute the supports the unknown parameters, $\sigma_{\epsilon}^2$ and $\xi$ are required and should be guessed beforehand.  To form a more accurate initial guess of the unkown parameters and explore the effect of chosen initial guess on the estimated supports several tests were performed. First consider equation \eqref{eq:EM-MMGFourier2} for estimating the disturbance covariance function. As mentioned before the power spectral densities are non negative, therefore the minimum value of $\mathcal F \{\mathbf E\left[ R_{y_ty_t}\right] \}$ and $\mathcal F \{\mathbf E\left[ R_{y_{t+1}y_{t+1}}\right]\}$ should be chosen as the higher limit for the initial guess of $\sigma^2_{\varepsilon}$. The minimum value of the power spectral density was found to be 0.23, Figure~\ref{fig:DisturbanceSupportExperiment} shows the support estimates for variyng  $\sigma^2_{\varepsilon}$ around the calculated limit. This figure shows that for values less than 0.23 the estimated support is close to the true one (see Figure~\ref{fig:BinaryDisturbanceWidthEstimation}(b)) while for values above 0.23 the shape of the disturbance covariance function is distorted. The estimated support of the covariance function convolved twice with the sensor kernel for  $\sigma^2_{\varepsilon}<$0.23 is shown in Figure~\ref{fig:BinaryDisturbanceWidthEstimation} (a), where the results were normalised and thresholded for values less than 0.01. By fitting a Guassian basis function to the result, and under the assumption that the width of the sensor, $\sigma_m^2$ were known, the width of the disturbance covariance function, $\sigma_d^2$ was calculated analytically using equation \eqref{eq:EM-AnalyticSupportCalculation}. Alternatively deconvolution can also be performed numerically to directly find the support as shown in Figure~\ref{fig:DisturbanceWidthEstimationCrossSection}.
